---
title: 'Bibliometric Analysis of European Research on Digital Divide: An Exploration of the Corporate Landscape'
author: "Luis Carlos Castillo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  beamer_presentation:
    includes:
      in_header: mystyle.tex
  slidy_presentation: default
  powerpoint_presentation: default
institute: |
  | University of Urbino
  | Ph.D. Program in Global Studies
editor_options:
  markdown:
    wrap: 72
bibliography: references.bib
header-includes:
  - \AtBeginEnvironment{CSLReferences}{\tiny}
biblio-style: apalike
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)
```

```{r Loading packages, include=FALSE}
library(tidyverse)
library(devtools)
library(here)
library(bibliometrix)
library(stringr)
library(readr)
library(visdat)
library(stringr)
library(dplyr)
library(readxl)
library(janitor)
library(ggplot2)
library(gridExtra)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(rmarkdown)
library(tidytext)
library(knitr)
library(qwraps2)
library(dplyr)
library(tables)
library(bibtex)


```

# Content I

1.  Motivation

2.  Objectives

3.  Digital Divide Overview

4.  Data

5.  Bibliometric Analysis

6.  Performance Analysis

    1.  Publications Vs Citations
    2.  Authors
    3.  Publications
    4.  Journals
    5.  Countries

# Content II

7.  Science Mapping

    1.  Citations Analysis
    2.  Co-citations Analysis
    3.  Bibliographic Coupling
    4.  Co-word Analysis

# 1. Motivation

-   The ubiquitous use of digital technologies has transformed many
    aspects of society and the economy, bringing potential benefits and
    drawbacks.

-   The Digital Europe program and the agenda to bridge the digital
    divide.

-   The few studies using the bibliometric method focus mainly on health
    sciences, computer science, and technology.

-   Data availability from three platforms containing references and
    citations from academic journals has stimulated this research
    initiative.

# 2. Objectives

-   Understand the intellectual structure within the domain of the
    digital divide.

-   Examine European research components' intellectual interactions,
    structural connections, and thematic relationships.

-   Explore the corporate digital divide among the collected corpus and
    identify trends and patterns within the literature.

# 3. The Digital Divide Overview I

-   The digital divide is also known as the digital gap, inequalities,
    or disparities.
-   The interaction with other existing gaps such as income, education,
    gender, generational, and regional, among others [@ragnedda2017].
-   The evolution of the concept has pointed out the phenomenon's
    complexity and the effects on the different layers of society and
    the economy [@vandijk2003; @ragnedda2017; @shakina2021].

# 3. The Digital Divide Overview II

-   The are four leading theories of the digital divide [@pick2016]:
    -   Adoption and Diffusion Theory (ADT)
    -   Van Dijk's Model of Digital Technology Access
    -   Unified Theory of Acceptance and Use Technology (UTAUT)
    -   Spatially Aware Technology Utilization Model (SATUM)

# 3. The Digital Divide Overview III

-   Waves of Research
    -   The first wave: Physical access to technology -\> possession of
        computers and access to the internet [@vandijk2003].

    -   The second wave: Usage of digital technologies and skills
        [@vandijk2006].

    -   The third wave: There needs to be more consensus among the
        scientific community while addressing the third-level digital
        divide:

        -   Sociological perspective [@ragnedda2017].

        -   Disparities in the ability to transform internet engagement
            into favorable offline outcomes [@vandeursen2015].

        -   The corporate digital divide [@shakina2021].

# 4. Data

```{r Total docs, include=F}
MM <- read_csv(here("Data", "Processed", "M_EU.csv"))
```

-   Specific search on the digital divide merging data from the Web of
    Science, Scopus, and Dimensions platforms.
-   Authors with European affiliations within the business, management,
    economics, technology, and computer science disciplines were
    included
-   After data cleaning, a total of `r nrow(MM)` unique documents from
    2000 to 2021 were incorporated.
-   The sample includes articles, book chapters, conferences, and
    proceedings.
-   The R programming language environment will be used during the data
    processing stage.

# 5. Bibliometric Analysis I

Following @donthu2021 and @Aria2017 bibliometric analysis:

-   Is a methodology that applies quantitative techniques to
    bibliographic data.
-   This technique allows researchers to uncover emerging trends
    identifying knowledge gaps in specific domains.
-   Is useful when analyzing a significant quantity of documents.
-   It offers three types of analysis: performance analysis, science
    mapping, and network analysis.

# 5. Bibliometric Analysis II

-   There are also limitations when using this methodology:

    -   Does not identify the purpose of citations.

    -   Heterogeneity in behavior citations among disciplines.

    -   Not all scientific output is published in bibliographic
        databases.

```{r Loading data, include=FALSE}
MM <- read_csv(here("Data", "Processed", "M_EU.csv"))
rownames(MM) <- MM$SR # using SR as row names
DA <- read_csv(here("Data", "Processed", "desc_analysis.csv"))
PD1p <- read_csv(here("Data", "Processed", "influ_arti_1p.csv"))
PD1p[, c(2,4)] <- lapply(PD1p[, c(2,4)], str_to_title)
PD2p <- read_csv(here("Data", "Processed", "influ_arti_2p.csv"))
PD3p <- read_csv(here("Data", "Processed", "influ_arti_3p.csv"))
COpro <- read_csv(here("Data", "Processed", "country_prod.csv"))


```

```{r descriptive, include=FALSE}

#kbl(DA)

options(qwraps2_markup = "markdown")
kable(DA, 
      caption = "Descriptive Analysis",
      col.names = c("Description",
                    "Period 1",
                    "Period 2",
                    "Period 3",
                    "Total")) %>% 
  kable_styling(latex_options  = "scale_down", font_size = 7, full_width = F) 



```

# References {.allowframebreaks}

```{r Line charts cite, include=F}

line_cite <- MM %>% group_by(PY) %>% # total citation per year
  summarise(totc = sum(TC)) %>%  
  ggplot(aes(x= PY, y= totc)) + 
  geom_line() + geom_vline(xintercept = c(2007, 2014),
                           linetype = "dotted",
                           color = "blue") +
  labs(title = "Total Citations per Year" ,
       x ="Years", 
       y = "Number of Citations") + 
  theme(text = element_text(size = 15))

line_docs <- MM %>% group_by(PY) %>% # total publications per year
  summarise(totd = n()) %>%  
  ggplot(aes(x= PY, y= totd)) + 
  geom_line() + geom_vline(xintercept = c(2007, 2014),                                         linetype = "dotted", 
                           color = "blue") +
  labs(title = "Total Publications per Year" ,
       x ="Years", 
       y = "Number of Publications") + 
  theme(text = element_text(size = 15))

```

```{r panel, include=F}
grid.arrange(line_docs, line_cite)
```

```{r Articles, include=F}


kable(PD1p, caption = "Most Influential Articles Between 2000-2007",
      col.names = c("Rank",
                    "Author",
                    "Year",
                    "Article Title",
                    "Total Citaions")) %>% 
  kable_styling(latex_options  = "scale_down", 
                font_size = 6, full_width = F) 


```
